Transient brightenings observed with multiple instruments

### 2021-09-22 Paper1.tex
to github

\documentclass{aastex62}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex62}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design 
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can envoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{The Kolsch of Data Sets}
\shortauthors{Kobelski et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%  \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Transient brightenings observed with multiple instruments}
\correspondingauthor{Adam R. Kobelski}
\email{adam.kobelski@mail.wvu.edu, ltarr2@gmu.edu, sjaeggli@nso.edu, sabrina.savage@nasa.gov}

\author{Adam R. Kobelski}
\affiliation{West Virginia University}

\author[0000-0002-8259-8303]{Lucas A. Tarr}
\affiliation{George Mason University}

\author{Sarah Jaeggli}
\affiliation{National Solar Observatory}

%% The \author command can take an optional ORCID.
\author{Sabrina Savage}
\affiliation{NASA Marshall Space Flight Center}
\begin{abstract}
Here is our abstract.  We did work

\end{abstract}
\keywords{The Sun, Radio, XRay, EUV}

\section{Introduction} \label{sec:intro}
Our work is awesome, here's why
\section{Observations} \label{sec:Obs}
\subsection{IBIS}
The IBIS data was reduced primarily using the pipeline code provided by NSO\footnote{Version 1.4, available here: https://www.nso.edu/telescopes/dunn-solar-telescope/dst-pipelines/}

\subsection{ALMA}

\subsection{Hinode}

\section{Coalignment} \label{sec:coalign}
Coaligning the various instruments was a challenge.  We did it like this:

\startlongtable
\begin{deluxetable}{c|cc}
\tablecaption{ApJ costs from 1991 to 2013\tablenotemark{a} \label{tab:table}}
\tablehead{
\colhead{Year} & \colhead{Subscription} & \colhead{Publication} \\
\colhead{} & \colhead{cost} & \colhead{charges\tablenotemark{b}}\\
\colhead{} & \colhead{(\$)} & \colhead{(\$/page)}
}
\colnumbers
\startdata
1991 & 600 & 100 \\
1992 & 650 & 105 \\
1993 & 550 & 103 \\
1994 & 450 & 110 \\
1995 & 410 & 112 \\
1996 & 400 & 114 \\
1997 & 525 & 115 \\
1998 & 590 & 116 \\
1999 & 575 & 115 \\
2000 & 450 & 103 \\
2001 & 490 &  90 \\
2002 & 500 &  88 \\
2003 & 450 &  90 \\
2004 & 460 &  88 \\
2005 & 440 &  79 \\
2006 & 350 &  77 \\
2007 & 325 &  70 \\
2008 & 320 &  65 \\
2009 & 190 &  68 \\
2010 & 280 &  70 \\
2011 & 275 &  68 \\
2012 & 150 &  56 \\
2013 & 140 &  55 \\
\enddata
\tablenotetext{a}{Adjusted for inflation}
\tablenotetext{b}{Accounts for the change from page charges to digital quanta in April, 2011}
\tablecomments{Note that {\tt \string \colnumbers} does not work with the 
vertical line alignment token. If you want vertical lines in the headers you
can not use this command at this time.}
\end{deluxetable}

\section{Displaying mathematics} \label{sec:displaymath}

\section{Revision tracking and color highlighting} \label{sec:highlight}

Authors sometimes use color to highlight changes to their manuscript in
response to editor and referee comments.  In \aastex\ new commands
have been introduced to make this easier and formalize the process.

The first method is through a new set of editing mark up commands that
specifically identify what has been changed.  These commands are
{\tt\string\added\{<text>\}}, {\tt\string\deleted\{<text>\}}, and
{\tt\string\replaced\{<old text>\}\{<replaced text>\}}. To activate these
commands the {\tt\string trackchanges} option must be used in the
{\tt\string\documentclass} call.  When compiled this will produce the
marked text in red.  The {\tt\string\explain\{<text>\}} can be used to add
text to provide information to the reader describing the change.  Its
output is purple italic font. To see how {\tt\string\added\{<important
added info>\}}, {\tt\string\deleted\{<this can be deleted text>\}},
{\tt\string\replaced\{<old data>\}\{<replaced data>\}}, and \break
{\tt\string\explain\{<text explaining the change>\}} commands will produce
\added{important added information}\deleted{, deleted text, and }
\replaced{old data}{and replaced data,} toggle between versions compiled with
and without the {\tt\string trackchanges} option.\explain{text explaining
the change}

A summary list of all these tracking commands can be produced at the end of
the article by adding the {\tt\string\listofchanges} just before the
{\tt\string\end\{document\}} call.  The page number for each change will be
provided. If the {\tt\string linenumbers} option is also included in the
documentcall call then not only will all the lines in the article be
numbered for handy reference but the summary list will also include the
line number for each change.

The second method does not have the ability to highlight the specific
nature of the changes but does allow the author to document changes over
multiple revisions.  The commands are {\tt\string\edit1\{<text>\}},
{\tt\string\edit2\{<text>\}} and {\tt\string\edit3\{<text>\}} and they
produce {\tt\string<text>} that is highlighted in bold red, italic blue and
underlined purple, respectively.  Authors should use the first command to
\edit1{indicated which text has been changed from the first revision.}  The
second command is to highlight \edit2{new or modified text from a second
revision}.  If a third revision is needed then the last command should be used 
\edit3{to show this changed text}.  Since over 90\% of all manuscripts are
accepted after the 3rd revision these commands make it easy to identify
what text has been added and when.  Once the article is accepted all the
highlight color can be turned off simply by adding the
{\tt\string\turnoffediting} command in the preamble. Likewise, the new commands
{\tt\string\turnoffeditone}, {\tt\string\turnoffedittwo}, and
{\tt\string\turnoffeditthree} can be used to only turn off the 
{\tt\string\edit1\{<text>\}}, {\tt\string\edit2\{<text>\}} and 
{\tt\string\edit3\{<text>\}}, respectively.

Similar to marking editing changes with the {\tt\string\edit} options there
are also the {\tt\string\authorcomments1\{<text>\}}, 
{\tt\string\authorcomments2\{<text>\}} and
{\tt\string\authorcomments3\{<text>\}} commands.  These produce the same
bold red, italic blue and underlined purple text but when the
{\tt\string\turnoffediting} command is present the {\tt\string<text>}
material does not appear in the manuscript.  Authors can use these commands
to mark up text that they are not sure should appear in the final
manuscript or as a way to communicate comments between co-authors when
writing the article.

\section{Software and third party data repository citations} \label{sec:cite}

The AAS Journals would like to encourage authors to change software and
third party data repository references from the current standard of a
footnote to a first class citation in the bibliography.  As a bibliographic
citation these important references will be more easily captured and credit
will be given to the appropriate people.

The first step to making this happen is to have the data or software in
a long term repository that has made these items available via a persistent
identifier like a Digital Object Identifier (DOI).  A list of repositories
that satisfy this criteria plus each one's pros and cons are given at \break
\url{https://github.com/AASJournals/Tutorials/tree/master/Repositories}.

In the bibliography the format for data or code follows this format: \\

\noindent author year, title, version, publisher, prefix:identifier\\

%% If you wish to include an acknowledgments section in your paper,
%% separate it off from the body of the text using the \acknowledgments
%% command.
\acknowledgments

We thank all the people that have made this AASTeX what it is today.  This
includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
for the new "modern" style design. Considerable help was provided via bug
reports and hacks from numerous people including Patricio Cubillos, Alex
Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
Gagne.

>>>>

\documentclass[twocolumn]{aastex62}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex62}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design 
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can invoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\unit}[1]{\ensuremath{\, \mathrm{#1}}}
\newcommand{\figref}[1]{Figure \ref{#1}}

\newcommand{\code}[1]{\ensuremath{\textsf{#1}}}
\newcommand{\lare}{\code{LARE}}
\newcommand{\scipy}{\code{scipy}}
\newcommand{\fnc}[1]{\code{#1}}
\newcommand{\removecomment}[1]{\textcolor{red}{#1}}
\newcommand{\secref}[1]{$\S$\ref{#1}}

% IBIS fitting macros
\newcommand{\halpha}{\ensuremath{H\alpha}}
\newcommand{\hfit}{\ensuremath{\halpha_\mathit{fit} }}
\newcommand{\linecenter}{\ensuremath{\lambda_0}}
\newcommand{\linew}{\ensuremath{\delta \lambda}}
\newcommand{\imin}{\ensuremath{I_\mathit{min}}}
\newcommand{\ihalf}{\ensuremath{I_\mathit{half}}}

% comments
\newcommand{\latcomment}[1]{\textcolor{red}{LAT: #1}}
\newcommand{\saj}[1]{\textcolor{cyan}{SAJ: #1}}
\newcommand{\ark}[1]{\textcolor{purple}{ARK: #1}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{The K\"{o}lsch of Data Sets}
\shortauthors{Kobelski et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%  \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{Transient brightenings observed with multiple instruments}
\correspondingauthor{Adam R. Kobelski}
\email{adam.kobelski@mail.wvu.edu}

\author[0000-0002-4691-1729]{Adam R. Kobelski}
\affiliation{NASA Marshall Space Flight Center}
\affiliation{West Virginia University}

\author[0000-0002-8259-8303]{Lucas A. Tarr}
\affiliation{National Solar Observatory}
%\email{ltarr@nso.edu}
\author[0000-0001-5459-2628]{Sarah Jaeggli}
\affiliation{National Solar Observatory}
%\email{sjaeggli@nso.edu}
\author{Nicholas Luber}
\affiliation{West Virginia University}
%% The \author command can take an optional ORCID.
\author[0000-0001-6102-6851]{Harry P. Warren}
\affiliation{Naval Research Laboratory}
%\email{harry.warren@nrl.navy.mil}
\author[0000-0002-6172-0517]{Sabrina Savage}
\affiliation{NASA Marshall Space Flight Center}
%\email{sabrina.savage@nasa.gov}

\begin{abstract}
%Transient brightenings (TBs) are ubiquitous features of the solar atmosphere across many length and energy scales, the most energetic of which manifest as large-class solar flares. TBs typically originate in regions of enhanced magnetic flux and are observed as increased emission across wavelengths from X-ray to radio, with notable dynamics on timescales of seconds to hours. Coronal TBs are often studied using Extreme Ultravioliet (EUV) and X-ray imaging and spectra. TBs likely originate from photospheric activity such as flux emergence, but are proximately driven by energy transfer through the chromosphere, either by convective waves, direct ejection of chromospheric material, or reconnection. Chromospheric and transition region observations of these events have only become routine in the last decade. 
%Chromospheric and transition region observations of these events have not been routine for the last few decades. 
New instruments sensitive to chromospheric radiation at X-ray, UV, Visible, IR, and sub-mm wavelengths have become available that significantly enhance our ability to understand the bi-directional flow of energy through the chromosphere. In this paper, we showcase and combine a new dataset utilizing a large number of these instruments to obtain multi-wavelength chromospheric observations capable of improving our understanding of the connectivity between the photosphere and the corona in the chromosphere via transient brightenings and wave signatures. This comprehensive study provides one of the most complete views of chromospheric activity related to small scale brightenings in the corona and chromosphere to date. SOME NUMBERS, SCIENCE CONCLUSIONS.

\end{abstract}
\keywords{The Sun, Radio, X-Ray, EUV}

\section{Introduction} \label{sec:intro}
The methods of transporting energy from the photosphere through the chromosphere to the million degree corona have been debated since the discovery of the hot corona \citep[][]{1933LyotMarshall, 1939Grotrian}. 
The underlying problem is that thermal conduction, which is very efficient in solar plasmas, will transport energy from the corona to the chromosphere, so the energy in the corona must constantly be resupplied.  
One of the early ideas for this transport of energy was via wave activity through hydrodynamic shocks \citep[][]{1949Schatzman} and later, once the central role of magnetic fields on the Sun was fully realized, by magnetoacoustic or Alfv\'en waves \citep{1961Osterbrock}. 
In this scenario, convective energy drives the waves which carry energy as they propagate upward through to the corona, and eventually deposit that energy as they cascade to small length-scales and heat the plasma through dissipation \citep{2014vanBallegooijenEA_FootpointMotion}.

Coronal waves have been observed in many forms. 
Large amplitude standing and propagating waves are caused by both confined flares and CMEs, and their properties are comparatively easy to detect and quantify \citep{2014LiuOfman_EUVwaves}. 
At the same time, many quiescent coronal structures exhibit continuous oscillatory power, detectable using Fourier transform or wavelet methods of longer time series \citep{Tomczyk:2009}, indicating that a broad spectrum of waves are present throughout the chromosphere and corona.
While the presence of waves is uncontested, where, by what mechanism, and how much wave energy may be dissipated to heat the coronal plasma is currently not well understood \citep{2014vanBallegooijenEA_FootpointMotion}.

As an alternative to wave heating, it has been posited that small-scale magnetic reconnection via nanoflares \citep[][]{1983Parker} could be responsible for the heating of the corona. 
It was thought that these nanoflares would manifest themselves as small scale brightenings in the corona, sometimes referred to as microflares or active region transient brightenings \citep[][]{1984LinEA_microflares, 1991Hudson, 1992ShimizuEA, 1995Shimizu}. 
\citet{1997GaryEA} determined that the small scale-brightenings exhibit the same signatures of particle acceleration as larger solar flares and concluded that many of the transient brightenings (TBs) were also products of magnetic reconnection. \latcomment{Reference some of the NuSTAR or Foxi work about this?} 
A key suggestion of the Parker nanoflare model was that the reconnection would occur due to substructure in the magnetic field lines, in which the observed loops consist of many unresolved braided magnetic strands. 
The concept of unresolved strands is in agreement with forward models of the observations \citep[e.g.][]{2012BrooksEA, 2014KobelskiEA_XRTTBs, 2014KobelskiMcKenzie_HiC}, and has been strongly suggested by direct observation in extreme ultraviolet (EUV) with the Hi-C sounding rocket \citep[][]{2013CirtainEA_HiC}.

Microflare research has largely focused on observable transients, which implies ``low-frequency'' active region heating wherein a larger plasma element, such as an overlying coronal loop, is heated significantly enough to show enhanced emission compared to the background and then notably cools over time \citep[][]{2015Klimchuk_CHoverview}. 
This scenario is in contrast to ``high-frequency'' heating wherein the observable plasma elements experience heating events fast enough that they appear at a sustained temperature and density, i.e. they are not allowed to cool or drain between successive heating events. 
Sometimes assumed in this latter paradigm is that the individual microflares occur on unresolved spatial and temporal scales, such that while individual strands may cool and/or drain, the conglomerated strand appears to have a steady average density and temperature \citep[e.g.][]{2013BrooksEA_LoopSize, 2014SubramanianEA_LowAndHighFrequency, 2016SchmelzEA}.

One of the best ways to follow how plasma flows through the chromosphere and corona is by using emission and absorption spectral measurements. 
For stable loops, raster scans from the \textit{Hinode} EUV Imaging Spectrograph (EIS) and the Interface Region Imaging Spectrograph (IRIS) have been used to better constrain the rate of heating quiescent regions of the Sun \citep[e.g.][]{2016BrooksWarren_NTWidths,2016TestaEA_ARLoopsIRISEIS, 2017GhoshEA_LoopsIRISEIS}. 
To measure flows during transient events requires fortuitous pointing and specific observations with minimal rastering. 
Here we present an ideal data set to study dynamic spectra of small scale, short lived coronal brightenings with coronal, chromospheric, and photospheric instrumentation. 
Such studies are crucial to understanding the flow of energy into the corona, as well as provide statistical insight into this coupled system during solar flares.

Much of the aforementioned work on TBs has focused on the \emph{coronal} observables, though recent instrumentation has shown evidence of chromospheric counterparts to microflaring \citep[][]{2016TestaEA_ARLoopsIRISEIS, 2017GhoshEA_LoopsIRISEIS}. 
The chromospheric response to large flares is well established in the form of chromospheric ablation from flare ribbons \citep[][]{2017Benz_LRSP}. 
The wave-driven chromospheric response to large flares has also been detected and investigated \citep[][and references within]{2014LiuOfman_EUVwaves, 2016RussellEA_Sunquakes}. 
What has eluded prior studies is a comprehensive insight into how wave motion through the chromosphere relates to the occurrence of small coronal flares, as well as how small flares drive chromospheric heating and waves. 
Evidence for this process is given by the partial temporal and spatial overlap of Ellerman bomb populations and UV burst populations, thought to be caused by energetic release at different heights \citep{2019Vissers, 2018Young}.
This feedback loop between waves and transients can inform the bi-directional flow of energy between the chromosphere and the corona.

In this paper, we present a unique, robust, and extensive data set with which to study the flow of energy through the chromosphere and the interplay between transients and wave activity. 
Even though the data set is of a quiescent solar region, it displays notable dynamics from the photosphere to the corona. 
This region is exemplary of the ubiquitous features found throughout the solar atmosphere during all phases of the solar cycle. 
The type of analysis we propose has been performed for active regions and strong plage, \emph{but not quiescent regions}. 
Since this data set probes each layer of the Sun in multiple wavelengths, heights, temperatures, and methodologies, it can provide multiple ground-truths and perspectives for which to compare to models of chromospheric energy flow and transfer in later papers.

The data set includes photospheric magnetic field information from the Helioseismic and Magnetic Imager \citep[HMI,][]{2012SchouEA_HMI} as well as imaging from the Atmospheric Imaging Assembly \citep[AIA,][]{2012LemenEA_AIA} on board the Solar Dynamics Observatory \citep[SDO,][]{2012PesnellEA_SDO}; photospheric magnetic field data from the Solar Optical Telescope \citep[SOT,][]{2008TsunetaEA_SOT}, coronal X-ray imaging from the X-Ray Telescope \citep[XRT,][]{2007GolubEA_XRT}, and EUV spectra from EIS \citep{2007CulhaneEA_EIS} on board the {\it Hinode} spacecraft \citep[][]{2007KosugiEA_Hinode}; chromospheric images and spectra from IRIS \citep{2014DePontieuEA_IRIS}; spectral images from the  Interferometric BIdimensional Spectropolarimeter \citep[IBIS,][]{2006Cavallini_IBIS} and infrared spectropolarimetry from the Facility InfraRed Spectropolarimeter \citep[FIRS,][]{2010JaeggliEA_FIRS} at the Dunn Solar Telescope (DST); and millimeter wave information from the Atacama Large Millimeter Array \citep[ALMA,][]{2009WootenThompson_ALMA, 2010HillsEA_ALMA2}.

In this paper, we describe the reduction of the imaging and spectral observations, as well as the co-alignment between instruments. 
We then interpret and compare activity between atmospheric layers, though a more thorough analysis is forthcoming.  
We give details of the observations in Section~\ref{sec:data}, their co-alignment in Section~\ref{sec:coalign} and their analysis in Section~\ref{sec:analysis}, with concluding remarks in \ref{sec:conclusion}.

\section{Data} \label{sec:data}
\subsection{Overview and Coordination}
The data sets presented in this work resulted from a large coordination campaign that was keyed to the ALMA observations and encompassed a suite of ground- and space-based facilities operated by different organizations.
The observations occurred during one of the first coordinated campaigns to support PI-led solar ALMA observations. Due to constraints in the ALMA scheduling, the exact timings and pointings could only be determined the day before the actual observations, with the result that there is not always complete temporal or spatial overlap between each facility.  
Given these constraints, the coverage is, in general, fairly good.

\figref{fig:coordination} presents an overview the temporal and spatial overlap between the various instrument channels during the time of the ALMA observations. 
In the upper panel we have ordered the instruments in the vertical direction roughly according to height in the solar atmosphere.
In addition to the times shown here, SOT, EIS, and XRT took observations of this same region for several days leading up to the ALMA observing window.
Fortuitously, NuSTAR also observed this region and detected two small flares around 19:00 and 19:30 UT \citep{2018Kuhar}.
The lower left panels show the approximate fields-of-view (FOV) of the various instruments overlaid on an AIA 193\AA{} image using the same colors as the upper panel, with the left showing the full Sun and the right a zoomed in region.
\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{figures/obs_timing}
    \includegraphics[width=0.48\linewidth]{figures/AIA193_FOVs.png}
    \includegraphics[width=0.48\linewidth]{figures/AIA193_FOVs_zoom.png}
    \caption{Overview of all observations around the ALMA observing window.  Upper plot: timing information, where instruments are ordered vertically roughly according to height in the solar atmosphere.  Gaps in each color band indicate data gaps in that data channel.  Lower panels: approximate FOVs for each instrument using the same colors as in the upper panel, overlaid on an SDO/AIA-193\AA{} context image.}
    \label{fig:coordination}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{figures/IBISimg0108.eps}
    \caption{Representative sample of co-aligned images. The SOT data has been rotated to align with the coordinate time of the IBIS data. The ALMA data ranges from $\pm$some number of K}
    \label{fig:coordination}
\end{figure}

\subsection{SDO/AIA}\label{sec:sdoaia}
AIA obtains full-disk images of the Sun every 12 seconds with 0.6\arcsec{} spatial sampling in a variety of visible, UV, EUV channels.
Observations from all AIA channels are available throughout the entire coordination period.
The Level 1 AIA data was downloaded from the Joint Science Operations Center (JSOC)\footnote{\url{http://jsoc.stanford.edu/}}, updated to Level 1.5 using \fnc{aia\_prep.pro} as described in the SDO Analysis Guide.
We also selected a subregion that fully encompassed the ALMA target using the SSW cutout service\footnote{\url{https://www.lmsal.com/get_aia_data/}; see also \S4.3 of the SDO Analysis Guide.} for a region approximately $300\arcsec\times300\arcsec$ for the duration of the other datasets (14:00-17:00 UT on 2017-03-21).
The 193 \AA\ channel of AIA was primarily used for co-alignment and to provide full-disk context for the other observations.  
The 193 \AA\ bandpass includes \ion{Fe}{12} and \ion{Fe}{24} lines which form in the corona and hot plasma at log(T)=6.2 and 7.3 respectively.

\subsection{SDO/HMI}
We used three days of intensity and line-of-site (LOS) magnetograms from the level 1.5 \texttt{hmi.M\_720s} and \texttt{hmi.Ic\_720s} series\footnote{JSOC query: \texttt{hmi.M\_720s[2017.03.19\_00:00:00\_TAI/3d]}, and similar for intensity.}.  
An area $\approx330\arcsec{}\times250\arcsec{}$ was tracked using solar rotation to understand the magnetic evolution of the region leading up to and throughout the coordinated observations.  
To ease later analysis, we derotated all HMI data so that the solar North-South axis aligned with columns of the data array, with North pointing upward, but kept the spatial scaling of the original HMI data.  
The typical extra step of spatially-rescaling the data to match AIA  has little benefit for use given that our various datasets include many different spatial samplings.

% Nick stuff, feel free to change at will, I was just getting my thoughts out.
\subsection{ALMA}
\paragraph{ALMA background} The Atacama Large Millimeter Array (ALMA) is a radio interferometer with current frequency coverage spanning 84 to 950 GHz. ALMA is constituted of 66 telescope dishes, 54 with a diameter of 12 meters, and 12 with a diameter of 7 meters. These 66 dishes are arranged as such to ensure that ALMA had suitable sensitivity to large scale diffuse emission, this is aided by the high density of centrally located dishes, and excellent resolution to small scale features, this is achieved with the dishes at high distance. The ALMA observations presented in this work were in the ALMA observing Band 3, which corresponds to a central frequency of 100 GHz, and a total bandwidth of 18 GHz about that central frequency. At this frequency and array configuration, our approximate resolution is 2$\arcsec$ on the sky. Our integration time used was 2 seconds and the entire observation, including the target field and calibrators, lasted for 1.03 hours.

\paragraph{ALMA calibration}
\paragraph{ALMA self-calibration}
\paragraph{ALMA issues with phase-center}

\subsection{DST/IBIS}
IBIS is a dual Fabry-Perot interferometer- (FPI-) based imaging spectropolarimeter that was mounted at the Dunn Solar Telescope.
The FPI cavity is tuned to transmit a narrow bandpass $(\approx 2.4\unit{pm})$, and the tuning is modulated to step the bandpass over the wavelength range of the line.
We used IBIS in spectal-only mode (no polarimetry) with a circular field stop of approximately 90\arcsec{} diameter.
We continuously sampled the \halpha{} line between 14:46-16:55 UT using 26 wavelength positions, with $\approx 12.5\unit{pm}$ spacing near line core and $\approx 19.1\unit{pm}$ spacing in the wings.  
Each narrow band image is paired with a strictly cotemporally acquired broad band continuum image taken in a nearby wavelength band at $660\unit{nm}$.
The broad band image is used for speckle reconstruction, self alignment of the narrow band images, and co-alignment between the IBIS data and other data series, e.g., to the HMI continua data series. \par

The IBIS data was reduced primarily using the pipeline code provided by NSO\footnote{Version 1.4, available here: \url{https://www.nso.edu/telescopes/dunn-solar-telescope/dst-pipelines/}.}.  
This process aligns the broad-band and narrow-band channels and accounts for detector dark counts, flat-fielding, and the spatially-dependent wavelength shift induced by the telecentric mount of the FPIs.  
Kevin Reardon provided several modified steps that better account for spatially- and spectrally-dependent fringes in the narrow band data due to the prefilter, as compared with the pipeline code\footnote{Reardon, private communication.  See documentation at \url{https://github.com/kreardon/IBIS.git}.}, which resulted in an improved estimate of the gain for each spatial and spectral point throughout the narrow band datacube.  
As a final calibration step, we used the KISIP code \citep{2008WoegerSPIE,2008WoegerEA_Speckle} to perform a speckle reconstruction of the data using the IBIS broad band images that are taken strictly co-temporally with the narrow band images; the broad band data is specifically designed for this purpose\citep{2008Cauzzi}.\par

We took several further steps for the IBIS preparation.  
To correct for the several arcsecond inaccuracy of the DST blind-pointing, slight rotation of solar-North with respect to the CCD pixel arrays, and the slight difference in plate-scale between the CCD X and Y directions, we rotated, shifted, and stretched the IBIS broad band data to match the granulation pattern in nearly co-temporal HMI continuum data at time 2017-03-21 15:46:36.
These parameters remained constant throughout the IBIS data series.
\par

\subsubsection{IBIS self alignment}\label{sec:ibisselfalign}
IBIS data in the spectral dimension is not strictly co-temporal: the time difference between successive wavelength steps is about $0.167\unit{s}$ and the cadence between images at a given wavelength is about $4.2\unit{s}$.
Our observations were taken during periods of moderate seeing, so the image sequence has some jitter, which became significant at times.  
To correct for this effect and spatially co-align all the IBIS data with itself we used a cross-correlation technique outlined here\footnote{The \texttt{chi2\_shift} method from Adam Ginsburg's \texttt{image\_registration} python package.  See \url{https://github.com/keflavich/image_registration}.}: 
\begin{enumerate}
    {\item We manually determined ``bad frames'' when AO lock was lost or a frame became significantly distorted, by inspecting the strictly co-temporal broad band images; these frames were assumed bad for all wavelengths in a given scan of the line.}
    {\item We generated a reference image by taking the running-average of the previous 5 registered ``good'' scans through the spectral line: at 26 images per scan, the average involves 130 broad band images.
    The initial average reference image was taken to be the average of the first spectral scan from the dataset.}
    {\item We used \texttt{chi2\_shift} to determine the spatial offset between each of the broad band images in a scan and the average reference image.}
    {\item If the frame was labeled ``good,'' the final registered broad band image for each wavelength was appended to running average.}
    {\item The measured offset was then saved, to be applied later to both the broad band image and the cotemporal narrow band image, which will co-align the entire data series (this last step has already been performed on the provided IBIS FITS files).}
\end{enumerate}

The above method allowed essentially all 46,800 frames to be co-aligned while being robust against the occasional loss of AO during brief periods of poor seeing.\par

\subsection{DST/FIRS}
During the coordinated observations, FIRS first conducted a raster observation from 14:46:47 to 15:00:54 UT (08:46:47 to 11:00:54 am MDT).  Then sit-and-stare observations were run almost continuously from 15:02:36 to 16:57:42 UT with small gaps for adjustment of the adaptive optics system.  During these observations, FIRS was configured to use the 40 $\mu$m single slit with the f/36 feed optics, which provide a slit width of 0.3 arcsec on the sky.  The vertical extent of the slit covered approximately 74 arcsec.  Only the 10830 \AA\ channel of FIRS was used, and the narrow band filter was removed to take advantage of the maximum wavelength coverage possible with the detector.  In this configuration the spectrograph was able to cover a 40 \AA\ bandpass centered at 10834 \AA.  This region contains the Si I and He I 1083 nm lines commonly used for spectropolarimetry, as well as several other solar and telluric lines.  The spectral dispersion of 3.86 pm/pixel is approximately equal to the spectral resolution of the instrument at this wavelength, based on laser profile measurements \citep{2011Jaeggli_PHD}.  An exposure time of 125 msec was used to keep counts within the range of linear behavior for the HgCdTe detector.  The liquid crystal variable retarders ran two repeats of a 4-state modulation sequence, and the time to execute a complete polarization measurement was about 4 seconds.
